The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-10-11 paper.tex
Added new subsection on state engineering.

The photonic states that are most commonly employed in linear optics protocols can be divided into Fock states (e.g single-photon), and entangled states, such as EPR, GHZ and cluster states. We will consider advances in each of these.

@@

\sihui{
\section{Quantum state engineering based on the multi-port Mach-Zehnder interferometer}
}

@@

Using time-bin encoding of optical qubits, the obvious question is how to perform operations upon them. In \cite{bib:Motes14}, a dual-loop architecture was presented for implementing arbitrary passive linear-optics on photonic pulse-trains with time-bin separation $\tau$, shown in Fig.~\ref{fig:FL_arch}. The inner loop has length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the 
number of optical modes). The architecture is controlled via three 
dynamically controlled beamsplitters. The first and last need only be on/off switches, whose sole purpose is to couple in the prepared pulse-train, 
keep it within the outer loop for the required duration, and then couple 
out of the outer loop, yielding the transformed pulse-train. The central 
beamsplitter must be able to implement arbitrary classically-controlled 
beamsplitter operations.

>>>>

The photonic states that are most commonly employed in linear optics protocols can be divided into Fock states (e.g single-photon), and entangled states, such as EPR, GHZ and cluster states. We will consider advances in each of these. \sihui{Quantum state engineering using quantum interferometers has also attracted some interest, and is discussed at the end of this section.}

@@

\sihui{
\subsection{Quantum state engineering based on the multi-port Mach-Zehnder interferometer}
Linear optical inteferometers have been used for quantum state engineering. One well-known example is that of optical state truncation, sometimes also referred to as quantum scissors, and it happens by way of a process known as projection synthesis [figure for this?].  Projection synthesis works by projecting an input state onto an output state by putting the former through a multiport interferometer, and then postselecting on a certain photon number output. Optical state truncation is a use of projection synthesis to use a continuous variable state represented in the Fock-state basis, $\ket{\phi}=\sum_{n=0}^\infty c_n\ket{n}$, to produce the normalized form of $\sum_{n=0}^d c_n\ket{n}$. The idea of projection synthesis was first conceived for the special case of $d=2$ \cite{bib:Pegg98, bib:Barnett99}, and later extended to $d=3$ \cite{bib:Koniorczyk2000}, and arbitrarily large $d$ \cite{bib:Miranowicz07, bib:Goyal13}. Notably, the scheme proposed in \cite{bib:Goyal13} uses multimode single photons and repeated uses of $d=2$ quantum scissors to extend the depth of truncation. 
}

@@

Using time-bin encoding of optical qubits, the obvious question is how to perform operations upon them. In \cite{bib:Motes14}, a dual-loop architecture was presented for implementing arbitrary passive linear-optics on photonic pulse-trains with time-bin separation $\tau$, shown in Fig.~\ref{fig:FL_arch}. The inner loop has lengtxh exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the 
number of optical modes). The architecture is controlled via three 
dynamically controlled beamsplitters. The first and last need only be on/off switches, whose sole purpose is to couple in the prepared pulse-train, 
keep it within the outer loop for the required duration, and then couple 
out of the outer loop, yielding the transformed pulse-train. The central 
beamsplitter must be able to implement arbitrary classically-controlled 
beamsplitter operations.
